Palomar 5 Gaps

### 2024-10-22 paper/main.tex
draft mode to full compile
proper implementation of the tail coordiantes figure

    Comparisons between the \texttt{reference} and \texttt{full} simulations were performed in the tail coordinate system. This system allows for consistent morphological comparisons by aligning the stream with the cluster's orbit. The coordinate system is based on the work of \citet{2004AJ....127.2753D} and is detailed in Fig.~\ref{appendix:TailCoordinates}. Briefly, the x' coordinate represents the position of a particle along the orbit relative to the globular cluster—whether it is ahead or behind the cluster. The y' coordinate measures the particle's distance within the orbital plane, where positive values indicate that the particle is farther from the Galactic center and negative values indicate that it is closer.

@@

  \section{Gap Detection} \label{sec:gap_detection}
    For each of the 50 simulations, we compare the final snapshots between the \texttt{reference} and \texttt{full} simulations using the tail coordinate system, as shown in Fig.~\ref{fig:TailCoordinates}. The vanilla simulations were only saved at the final timestamps, thus from Eq.\ref{eq:data_volume_estimate} where $N_ts$=1, leading to a data volumne of about one hundred messily megabytes. We inspect these differences by generating 2D density maps of the streams. Additionally, we marginalize over the $y'$-coordinate to produce 1D density profiles along the $x'$-axis. These comparisons are shown in the results section (see Fig.~\ref{fig:profiles}).
    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{figures/along_orbit_coordinate_system-approved.png}
      \caption{Tail coordinates}
      \label{fig:TailCoordinates}
    \end{figure}

>>>>

    Comparisons between the \texttt{reference} and \texttt{full} simulations were performed in the tail coordinate system. This system allows for consistent morphological comparisons by aligning the stream with the cluster's orbit. The coordinate system is based on the work of \citet{2004AJ....127.2753D} and is shown in Fig.~\ref{fig:TailCoordinates}. Briefly, the x' coordinate represents the position of a particle along the orbit relative to the globular cluster—whether it is ahead or behind the cluster. The y' coordinate measures the particle's distance within the orbital plane, where positive values indicate that the particle is farther from the Galactic center and negative values indicate that it is closer.

@@

  \section{Gap Detection} \label{sec:gap_detection}
    For each of the 50 simulations, we compare the final snapshots between the \texttt{reference} and \texttt{full} simulations using the tail coordinate system, as shown in Fig.~\ref{fig:TailCoordinates}. The vanilla simulations were only saved at the final timestamps, thus from Eq.\ref{eq:data_volume_estimate} where $N_ts$=1, leading to a data volumne of about one hundred messily megabytes. We inspect these differences by generating 2D density maps of the streams. Additionally, we marginalize over the $y'$-coordinate to produce 1D density profiles along the $x'$-axis. These comparisons are shown in the results section (see Fig.~\ref{fig:profiles}).
    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{along_orbit_coordinate_system-approved.png}
      \caption{Tail coordinates}
      \label{fig:TailCoordinates}
    \end{figure}
